---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# csabounds

The csabounds package allows the user to obtain tight bounds on distributional treatment effect parameters that depend on the joint distribution of treated and untreated potential outcomes -- the joint distribution is not identified under standard identifying assumptions such as selection on observables or even when experimental data is available.  Using the package requires three periods of panel data and the results follow under the Copula Stability Assumption.  More details about the method can be found in Callaway (2017).

## Installation

You can install csabounds from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bcallaway11/csabounds")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
